Mapping plant-pollinator interactions across Europe

### 2023-12-12 Manuscript/Ms.qmd
adding levels of site id progamatically in metadata

Pollinators play a crucial role in maintaining Earth's terrestrial biodiversity and human food production by mediating sexual reproduction for most flowering plants. However, their diversity and role as pollinators are increasingly compromised by rapid human-induced environmental changes. One of the major challenges for pollinator conservation, is the lack of robust generalisable data across space and time. Here, we present a dataset of plant-pollinator interactions at European level that consists of `r study_number` studies compiled during the years xxx and xxxx.

Here, we have tried to generate a comprehensive dataset of plant-pollination interactions to build the first European metaweb of plant and pollinators and explore their general patterns.

we have done a strong collaborative effort in unifying plant-pollinator studies at continent level to elucidate general patterns of plant-pollinator interactions and set a baseline for future ecological research. Thus, we explore the first time an European metaweb of plant-pollinator interactions

>>>>

Pollinators play a crucial role in maintaining Earth's terrestrial biodiversity and human food production by mediating sexual reproduction for most flowering plants. However, their diversity and role as pollinators are increasingly compromised by rapid human-induced environmental changes. One of the major challenges for pollinator conservation, is the lack of robust generalisable data across space and time. Here, we present a dataset of plant-pollinator interactions at European level that consists of `r study_number` studies that cover `r country_number` countries and comprised over a million of interactions between plants and pollinators.
